The \dealii Library, Version 9.2

### 2020-05-26 9.2/paper.tex
Language fix.
Add one missing entry.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Improved performance of symbolic framework}
\label{subsec:symbdiff}

@@

\dealii is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
% updated 5/11/2020 MM
\todo[inline]{TODO: remove authors of paper}
Pasquale Africa,
Ashna Aggarwal,
Giovanni Alzetta,
Mathias Anselmann,
Daniel Arndt,
Wolfgang Bangerth,
Kirana Bergstrom,
Manaswinee Bezbaruah,
Bruno Blais,
Benjamin Brands,
Yong-Yong Cai,
Fabian Castelli,
Thomas C. Clevenger,
Katherine Cosburn,
Denis Davydov,
Elias Dejene,
Stefano Dominici,
Brett Dong,
Luel Emishaw,
Marc Fehling,
Niklas Fehn,
Rebecca Fildes,
Menno Fraters,
Andres Galindo,
Daniel Garcia-Sanchez,
Rene Gassmoeller,
Melanie Gerault,
Nicola Giuliani,
Brandon Gleeson,
Anne Glerum,
Krishnakumar Gopalakrishnan,
Graham Harper,
Mohammed Hassan,
Nicole Hayes,
Bang He,
Johannes Heinz,
Timo Heister,
Luca Heltai,
Jiuhua Hu,
Lise-Marie Imbert-Gerard,
Manu Jayadharan,
Daniel Jodlbauer,
Marie Kajan,
Guido Kanschat,
Alexander Knieps,
Martin Kronbichler,
Paras Kumar,
Konstantin Ladutenko,
Charu Lata,
Adam Lee,
Wenyu Lei,
Matthias Maier,
Katrin Mang,
Mae Markowski,
Franco Milicchio,
Adriana Morales Miranda,
Peter Munch,
Bob Myhill,
Emily Novak,
Omotayo Omosebi,
Alexey Ozeritskiy,
Jean-Paul Pelteret,
Rebecca Pereira,
Geneva Porter,
Laura Prieto Saavedra,
Reza Rastak,
Roland Richter,
Jonathan Robey,
Irabiel Romero,
Matthew Russell,
Tonatiuh Sanchez-Vizuet,
Natasha S. Sharma,
Doug Shi-Dong,
Konrad Simon,
Stephanie Sparks,
Sebastian Stark,
Simon Sticko,
Jan Philipp Thiele,
Jihuan Tian,
Ignacio Tomas,
Sara Tro,
Bruno Turcksin,
Ferdinand Vanmaele,
Zhuoran Wang,
David Wells,
Michal Wichrowski,
Julius Witte,
Winnifried Wollner,
Ming Yang,
Mario Zepeda Aguilar,
Wenjuan Zhang,
Victor Zheng.

@@

W.~Bangerth and T.~Heister were also partially supported by award DMS-1821210.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Improved performance of the symbolic differentiation framework}
\label{subsec:symbdiff}

@@

\dealii is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
%
% Uwe Koecher doesn't usually show up in the changelog, but
% we should make sure he's listed.
%
% 9.2: updated 5/11/2020 MM
\todo[inline]{TODO: remove authors of paper}
Pasquale Africa,
Ashna Aggarwal,
Giovanni Alzetta,
Mathias Anselmann,
Daniel Arndt,
Wolfgang Bangerth,
Kirana Bergstrom,
Manaswinee Bezbaruah,
Bruno Blais,
Benjamin Brands,
Yong-Yong Cai,
Fabian Castelli,
Thomas C. Clevenger,
Katherine Cosburn,
Denis Davydov,
Elias Dejene,
Stefano Dominici,
Brett Dong,
Luel Emishaw,
Marc Fehling,
Niklas Fehn,
Rebecca Fildes,
Menno Fraters,
Andres Galindo,
Daniel Garcia-Sanchez,
Rene Gassmoeller,
Melanie Gerault,
Nicola Giuliani,
Brandon Gleeson,
Anne Glerum,
Krishnakumar Gopalakrishnan,
Graham Harper,
Mohammed Hassan,
Nicole Hayes,
Bang He,
Johannes Heinz,
Timo Heister,
Luca Heltai,
Jiuhua Hu,
Lise-Marie Imbert-Gerard,
Manu Jayadharan,
Daniel Jodlbauer,
Marie Kajan,
Guido Kanschat,
Alexander Knieps,
Uwe K{\"o}cher,
Martin Kronbichler,
Paras Kumar,
Konstantin Ladutenko,
Charu Lata,
Adam Lee,
Wenyu Lei,
Matthias Maier,
Katrin Mang,
Mae Markowski,
Franco Milicchio,
Adriana Morales Miranda,
Peter Munch,
Bob Myhill,
Emily Novak,
Omotayo Omosebi,
Alexey Ozeritskiy,
Jean-Paul Pelteret,
Rebecca Pereira,
Geneva Porter,
Laura Prieto Saavedra,
Reza Rastak,
Roland Richter,
Jonathan Robey,
Irabiel Romero,
Matthew Russell,
Tonatiuh Sanchez-Vizuet,
Natasha S. Sharma,
Doug Shi-Dong,
Konrad Simon,
Stephanie Sparks,
Sebastian Stark,
Simon Sticko,
Jan Philipp Thiele,
Jihuan Tian,
Ignacio Tomas,
Sara Tro,
Bruno Turcksin,
Ferdinand Vanmaele,
Zhuoran Wang,
David Wells,
Michal Wichrowski,
Julius Witte,
Winnifried Wollner,
Ming Yang,
Mario Zepeda Aguilar,
Wenjuan Zhang,
Victor Zheng.

@@

W.~Bangerth and T.~Heister were also partially supported by award DMS-1821210.
\todo[inline]{Need to add FRES project}
